# B48


```{r ,include=FALSE}
library(Rose)
library(ggplot2)
library(plotly)
library(knitr)
require(tikzDevice)
df <- data.frame(x = 1:5, y = 1:5)
f1 <- function(df) {
  gg <- ggplot(df, aes(x,y)) + geom_point()
  assign("ggp", plotly::ggplotly(gg), envir=parent.frame())
  #ggp
  df    # NOT returning a plot
}
res1 <- f1(df)
ggp   # Let knit handle the plot
myplotly(ggplot())
```

```{r, echo=FALSE, results='asis'}
file<-paste0("/home/garofalo/analysis/data_LIBE_gm2/out/LIBE_B48.dat_output")
mt<-read_df(file)
all_obs<- get_all_corr(mt)
df<-add_corr_to_df(string =paste0("M_{PS}"),
                    all_obs=all_obs,mt=mt,df = NULL,
                    log=FALSE, number =NULL, nudge=0)

df<-add_corr_to_df(string =paste0("M_{K}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)

df<-add_corr_to_df(string =paste0("M_{K1}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)
df<-add_corr_to_df(string =paste0("M_{K2}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)

gg<- plot_df_corr_ggplot(df,width = 0.01)
fig<- myplotly(gg,"","t","$M_{PS}$",  to_print=TRUE )


```


The correction to the pion correlator is 
$$
C(t)= C_0(t) + e^2\delta_e C(t)
$$

We define the discrete second derivative $\nabla_e^2f(e)=(f(e)-2f(0)+f(-e))/e^2$.
due to the different quark charges we need to compute the derivative respect the two
quark lines separately
$$
\delta_e C = \frac{1}{2}[e_u^2 \nabla^2_{e1} C + e_d^2 \nabla^2_{e2} C 
  + e_u e_d(\nabla^2_{e} C - \nabla^2_{e1} C  -\nabla^2_{e2} C) ]
$$
with $\nabla_{e1}$ is the derivative respect only one leg.
To compute the correction respect to the effective mass $M(e)=M_0+\delta M$ we use the formula
$$
\delta M(t)=\left( \frac{\delta C(t+1)}{C_0(t)} -\frac{\delta C(t)}{C_0(t) } \right)\frac{1}{[(T/2-t-1) \tanh(M_0(T/2-t-1))-(T/2-t) \tanh(M_0(T/2-t)) ]}
$$ {#eq-dm}


```{r, echo=FALSE, results='asis'}
file<-paste0("/home/garofalo/analysis/data_LIBE_gm2/out/LIBE_B48.dat_output")
mt<-read_df(file)
all_obs<- get_all_corr(mt)
df<-add_corr_to_df(string =paste0("Delta_e_M_{PS}"),
                    all_obs=all_obs,mt=mt,df = NULL,
                    log=FALSE, number =NULL, nudge=0)

df<-add_corr_to_df(string =paste0("Delta_e_M_{Kp}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)
df<-add_corr_to_df(string =paste0("Delta_e_M_{K0}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)

gg<- plot_df_corr_ggplot(df,width = 0.01)
fig<- myplotly(gg,"","t","$\\Delta_e M_{PS}$",  to_print=TRUE )


```

## exchange only

Below we compute only 
$$
\delta_{exc} C\frac{1}{2}e_u e_d(\nabla^2_{e} C - \nabla^2_{e1} C  -\nabla^2_{e2} C)
$$
and we plot $\delta_{exc} C/C$

```{r, echo=FALSE, results='asis'}
file<-paste0("/home/garofalo/analysis/data_LIBE_gm2/out/LIBE_B48.dat_output")
mt<-read_df(file)
all_obs<- get_all_corr(mt)
df<-add_corr_to_df(string =paste0("Delta_e_exc_fit_M_{PS}"),
                    all_obs=all_obs,mt=mt,df = NULL,
                    log=FALSE, number =NULL, nudge=0)


gg<- plot_df_corr_ggplot(df,width = 0.01)
fig<- myplotly(gg,"","t","$\\delta_{exc} C(t)/C_0(t)$",  to_print=TRUE )

```

using formula (@eq-dm) using $M_0(t)$ and $M_0$ from the plateau fit we get 


```{r, echo=FALSE, results='asis'}
file<-paste0("/home/garofalo/analysis/data_LIBE_gm2/out/LIBE_B48.dat_output")
mt<-read_df(file)
all_obs<- get_all_corr(mt)
df<-add_corr_to_df(string =paste0("Delta_e_exc_M_{PS}"),
                    all_obs=all_obs,mt=mt,df = NULL,
                    log=FALSE, number =NULL, nudge=0)
df<-add_corr_to_df(string =paste0("Delta_e_exc_mefft_M_{PS}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)


gg<- plot_df_corr_ggplot(df,width = 0.01)
fig<- myplotly(gg,"","t","$\\Delta_\\mu M_{PS}$",  to_print=TRUE )

```

## mass

The correction to the pion correlator due to a change of mass $\mu_u= \mu_{iso}+\delta \mu_u$ and $\mu_d=\mu_{iso}+\delta \mu_d$
$$
C(t)= C_0(t) + \delta\mu_u\delta_{\mu_u} C(t) +\delta\mu_d\delta_{\mu_d} C(t)
$$
since $\delta_{\mu_u} C = \delta_{\mu_d} C \equiv\delta_{\mu} C$ we car rewrite
$$
C(t)= C_0(t) + 2(\mu_{ud} -\mu_{iso}  )   \delta_{\mu} C(t) 
$$
where $\delta_\mu C$ is computed with the insertions 

```{r, echo=FALSE, results='asis'}
file<-paste0("/home/garofalo/analysis/data_LIBE_gm2/out/LIBE_B48.dat_output")
mt<-read_df(file)
all_obs<- get_all_corr(mt)
df<-add_corr_to_df(string =paste0("Delta_mu_u_M_{PS}"),
                    all_obs=all_obs,mt=mt,df = NULL,
                    log=FALSE, number =NULL, nudge=0)

df<-add_corr_to_df(string =paste0("Delta_mu_d_M_{PS}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)

df<-add_corr_to_df(string =paste0("Delta_mu_u_M_{Kp}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)

df<-add_corr_to_df(string =paste0("Delta_mu_u_M_{K0}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)


gg<- plot_df_corr_ggplot(df,width = 0.01)
fig<- myplotly(gg,"","t","$\\Delta_\\mu M_{PS}$",  to_print=TRUE )


```

## critical mass

The correction to the pion correlator due to a change of critical mass $m_0$
$$
C(t)= C_0(t) + \delta m_0^u\delta_{m_0} C(t)+\delta m_0^d\delta_{m_0} C(t)
$$
where $\delta_{m_0} C$ is computed with the insertions 


```{r, echo=FALSE, results='asis'}
file<-paste0("/home/garofalo/analysis/data_LIBE_gm2/out/LIBE_B48.dat_output")
mt<-read_df(file)
all_obs<- get_all_corr(mt)
df<-add_corr_to_df(string =paste0("Delta_m0_u_M_{PS}"),
                    all_obs=all_obs,mt=mt,df = NULL,
                    log=FALSE, number =NULL, nudge=0)
df<-add_corr_to_df(string =paste0("Delta_m0_d_M_{PS}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)
df<-add_corr_to_df(string =paste0("Delta_m0_u_M_{Kp}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)
df<-add_corr_to_df(string =paste0("Delta_m0_u_M_{K0}"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)


gg<- plot_df_corr_ggplot(df,width = 0.01)
fig<- myplotly(gg,"","t","$\\Delta_{m_0} M_{PS}$",  to_print=TRUE )


```

## critical mass determination

We consider the correlator VP:

$$
 C^{VP}=\langle \, \left( \bar u_+ \gamma_0 d_-  \right) (x) \, \left(  \bar d_- \gamma_5 u_+  \right) (0) \, \rangle
$$
expanding in the counterterms, after noticing that it does not depend on $\mu$, we get
$$
C^{VP} =C^{VP}_0 + e^2 \delta_e C^{VP}+2(m_0^{ud}-m_0^{iso})\delta_{m0}C^{VP}\,.
$$
From the requirement $C^{VP}=0$  we compute 
$$
m_0^{ud}-m_0^{iso} =  e^2 \frac{\delta_e C^{VP}}{2\delta_{m0}C^{VP}}
$$


```{r, echo=FALSE, results='asis'}

file<-paste0("/home/garofalo/analysis/data_LIBE_gm2/out/LIBE_B48.dat_output")
mt<-read_df(file)
all_obs<- get_all_corr(mt)
df<-NULL
# df<-add_corr_to_df(string =paste0("VP"),
#                     all_obs=all_obs,mt=mt,df = NULL,
#                     log=FALSE, number =NULL, nudge=0)
df<-add_corr_to_df(string =paste0("VP_im"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)

df<-add_corr_to_df(string =paste0("Delta_e_VP"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)

df<-add_corr_to_df(string =paste0("Delta_m0u_VP"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)

df<-add_corr_to_df(string =paste0("Delta_m0d_VP"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)

# df<-add_corr_to_df(string =paste0("Delta_muu_VP"),
#                     all_obs=all_obs,mt=mt,df = df,
#                     log=FALSE, number =NULL, nudge=0)

# df<-add_corr_to_df(string =paste0("Delta_mud_VP"),
#                     all_obs=all_obs,mt=mt,df = df,
#                     log=FALSE, number =NULL, nudge=0)

df<-add_corr_to_df(string =paste0("dm0_cr"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0, rename = "$m_0^{ud}-m_0^{iso}$")

df<-add_corr_to_df(string =paste0("dm0_cr_nabla"),
                    all_obs=all_obs,mt=mt,df = df,
                    log=FALSE, number =NULL, nudge=0)
fit<-get_full_res("dm0_cr_nabla", all_obs,mt)
# cat( fit[1,1]/(4*pi/137.03599)*2/5*9, fit[1,2]/(4*pi/137.03599)*2/5*9)
gg<- plot_df_corr_ggplot(df,width = 0.01)
fig<- myplotly(gg,"","t","VP",  to_print=TRUE )


```


## Approximated System

Here we want to solve the system taking the lattice spacing from ISOQCD:
$$
\begin{pmatrix}
\delta_{\mu_u}M_{\pi^+} & \delta_{\mu_d}M_{\pi^+}  &0\\
\delta_{\mu_u}M_{K^+}   & 0                        &\delta_{\mu_s}M_{K^+} \\
0                       & \delta_{\mu_d}M_{K^0}    &\delta_{\mu_s}M_{K^0} \\
\end{pmatrix}
\begin{pmatrix}
\delta{\mu_u}\\
\delta{\mu_d}\\
\delta{\mu_s}
\end{pmatrix}
=
\begin{pmatrix}
M_{\pi^+}^{exp}-M_{\pi^+}^{iso}-e^2\delta_e M_{\pi^+}\\
M_{K^+}^{exp}-M_{K}^{iso}-e^2\delta_e M_{K^+}\\
M_{K^0}^{exp}-M_{K}^{iso}-e^2\delta_e M_{K^0}\\
\end{pmatrix}
-
\begin{pmatrix}
\delta_{m_u}M_{\pi^+} & \delta_{m_d}M_{\pi^+}  &0\\
\delta_{m_u}M_{K^+}   & 0                        &\delta_{m_s}M_{K^+} \\
0                       & \delta_{m_d}M_{K^0}    &\delta_{m_s}M_{K^0} \\
\end{pmatrix}
\begin{pmatrix}
\delta{m_u}\\
\delta{m_d}\\
\delta{m_s}
\end{pmatrix}
$$
 we get

$$
a \delta mu_u = -0.000458078  \pm  0.000125146 \\
a \delta mu_d = 0.000484155  \pm 3.26229e-05  \\
a \delta mu_s = -0.00149157  \pm 0.000117523  \\
\delta mu_u[Mev] = -1.13599 \pm  0.310483  \\
\delta mu_d[Mev] = 1.20066 \pm  0.08049  \\
\delta mu_s[Mev] = -3.69897 \pm  0.286266  \\
$$
